Rusty Linux: Advances in Rust for Linux Kernel Development

### 2024-08-30 paper.tex
Clean ups for camera ready

    The C programming language has the advantage of 40 years of improvements and lessons learned regarding how to write fast code. Rust, being a new language, still has many unexplored areas regarding how to write fast code, especially in kernel space. Therefore, we want to explore the performance implications of Rust for kernel development in terms of throughput, latency, and resource utilization.
    \item \textbf{RQ3: What are the major challenges and limitations when developing operating system kernels in Rust?}% particularly in comparison to other languages?

@@

We employed a robust multi-step search strategy across four databases: ACM Digital Library,
IEEE Xplore, Scopus, and Springer Link to find all the current research. 
%These databases cover a wide range of current software engineering and computer science literature. 
We leveraged the advanced search features of all three databases to search the titles and abstracts for
keywords using boolean search operators.

@@

Finally, researchers have taken existing Unikernels written in C and ported them to Rust. Unikernels are designed to do one thing
and one thing only, thus limiting the complexity that a general-purpose operating system has to
deal with~\cite{Madhavapeddy2014-zw}. This reduced complexity allowed  Lankes et al.~\cite{Lankes2019-cm} to take HermitCore and rewrite it in Rust. The new
Unikernel named RustyHermit consists of only 3.27\% unsafe Rust, with the rest of the code base consisting of safe Rust, dramatically decreasing the surface area where memory errors could originate.

@@

% In conducting this systematic literature review on the use of Rust for operating system development,
% several potential threats to validity must be acknowledged. These threats are categorized into
% internal, external, and conclusion validity, each presenting distinct challenges to the robustness
% and reliability of our findings.

\textit{\textbf{Internal Threats.}} 
%Internal validity refers to the degree to which the review accurately establishes
%causal relationships.
Potential internal threats include:

\begin{itemize}
  %\item Publication Bias: Studies demonstrating positive outcomes of using Rust for kernel
    %development may be more likely to be published and cited, leading to an overestimation of its
    %benefits.
  \item \textit{Quality of Studies:} The methodological rigor of the included studies varies, and some may
    suffer from design flaws or biases that were not adequately controlled for, thus affecting the
    reliability of their findings.
  \item  \textit{Selection Criteria:} The inclusion and exclusion criteria for selecting relevant studies might inadvertently bias the review towards certain types of research, such as those reporting successful integration while underrepresenting studies detailing challenges and failures.
\end{itemize}

\textit{\textbf{External Threats.}} 
%External validity pertains to the generalizability of the review's findings
%beyond the specific context of the reviewed studies. 
Threats to external validity include:

@@

\textbf{\textit{Conclusion Threats}.}
%Conclusion validity involves the degree to which the conclusions drawn from the
%review are credible and supported by the data.
Potential conclusion threats include:

@@

We made efforts to minimize this through predefined criteria and multiple reviewers, but some
degree of subjectivity is inevitable.  In addressing these threats, we employed rigorous methods for
study selection, data extraction, and analysis, and we remain transparent about the
limitations. 
%Future studies could mitigate these threats further by incorporating a broader range of sources, using more precise definitions, and employing meta-analytic techniques to quantitatively synthesize findings. 
Despite these threats, our results provide a valuable synthesis of the current
state of research on the use of Rust in kernel development, highlighting both its potential benefits
and the challenges that need to be addressed.

>>>>

    The C programming language has the advantage of 40 years of improvements and lessons learned regarding how to write fast code. Rust, being a new language, still has many unexplored areas regarding how to write fast code, especially in kernel space. Therefore, we want to explore the performance implications of Rust for kernel development in terms of throughput, latency, and resource utilization.
    \item \textbf{RQ3: What are the major challenges and limitations when developing operating system kernels in Rust?}

@@

We employed a robust multi-step search strategy across four databases: ACM Digital Library,
IEEE Xplore, Scopus, and Springer Link to find all the current research.
We leveraged the advanced search features of all three databases to search the titles and abstracts for
keywords using boolean search operators.

@@

Finally, researchers have taken existing unikernels written in C and ported them to Rust. Unikernels are designed to do one thing
and one thing only, thus limiting the complexity that a general-purpose operating system has to
deal with~\cite{Madhavapeddy2014-zw}. This reduced complexity allowed  Lankes et al.~\cite{Lankes2019-cm} to take HermitCore and rewrite it in Rust. The new
Unikernel named RustyHermit consists of only 3.27\% unsafe Rust, with the rest of the code base consisting of safe Rust, dramatically decreasing the surface area where memory errors could originate.

@@

\textit{\textbf{Internal Threats.}} Potential internal threats include:

\begin{itemize}
  \item \textit{Quality of Studies:} The methodological rigor of the included studies varies, and some may
    suffer from design flaws or biases that were not adequately controlled for, thus affecting the
    reliability of their findings.
  \item  \textit{Selection Criteria:} The inclusion and exclusion criteria for selecting relevant studies might inadvertently bias the review towards certain types of research, such as those reporting successful integration while underrepresenting studies detailing challenges and failures.
\end{itemize}

\textit{\textbf{External Threats.}} Threats to external validity include:

@@

\textbf{\textit{Conclusion Threats}.} Potential conclusion threats include:

@@

We made efforts to minimize this through predefined criteria and multiple reviewers, but some
degree of subjectivity is inevitable.  In addressing these threats, we employed rigorous methods for
study selection, data extraction, and analysis, and we remain transparent about the
limitations. Despite these threats, our results provide a valuable synthesis of the current
state of research on the use of Rust in kernel development, highlighting both its potential benefits
and the challenges that need to be addressed.
